A holomorphic approach to membranes and fivebranes

### 2022-07-19 fivebranes/intro.tex
updated intro

Introduced by Witten \cite{} and further developed by Costello \cite{}, twisting refers to a fixed-point construction for field theories equipped with the action of a supersymmetry algebra. Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge - the result is a theory on which the translations in the image of the supercharge act homotopically trivially. Every supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions. One of the insights of \cite{} was that superconformal indices counts exactly local operators in the minimal twist.

The six-dimensional $\cN=(2,0)$ supersymmetric theory

In this paper we apply the proposal of \textit{twisted holography} introduced by Costello and Li in \cite{CLsugra} to access the worldvolume theory on a stack of fivebranes in minimally twisted eleven-dimensional supergravity.
Twisted holography shares, in many ways, the spirit of familiar gauge-gravity dualities such as the AdS/CFT correspondence. 
The heart of the program relates the algebra of observables of the bulk gravity theory, which lives on a twisted version of AdS space, to the observables of the worldvolume theory living on a defect, which plays the role of the CFT.

>>>>

Introduced by Witten \cite{} and further developed by Costello \cite{}, twisting refers to a fixed-point construction for field theories equipped with the action of a supersymmetry algebra. Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge - the result is a theory on which the translations in the image of the supercharge act homotopically trivially. Every supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions.

One of the insights of \cite{} was that superconformal indices count exactly local operators in the minimal twist - accordingly, we may think of the algebra of local operators in the minimal twist as \textit{categorifying} the superconformal index. Moreover, the algebra of local operators is part of the richer structure of a \textit{factorization algebra}. Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set.

A principal goal of the present paper is to initiate a study of factorization algebras associated to the minimal twists of the six-dimensional $\mc N=(2,0)$ and three-dimensional $\mc N=8$ superconformal field theories. However, the six-dimensional $\cN=(2,0)$ supersymmetric theory remains quite elusive - it is non-lagrangian, and outside of the abelian case, is not known to admit a field-realization. In light of this, we propose to access the minimal twist and its local operators via \textit{twisted holography}.

\subsection{Twisted Holography}
Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of twists. The main objects involved are factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes therein.

A more concrete, albeit informal, statement is as follows. Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of some bulk gravitational theory. Suppose we in addition have a stack of $N$ branes, wrapping a submanifold $\iota: Y\into X$, whose worldvolume theory has a factorization algebra of observables $\Obs^{N}_{brane}$.

\begin{}[Twisted Holographic Principle]
  There is a map of factorization algebras
  \[
        (\iota^{*}\Obs_{grav})^{!}\to \Obs^{N}_{brane}
  \]

      that becomes an equivalence in the large $N$ limit.
    \end{}

    This statement has been tested in many examples \cite{}.

\subsection{Infinite dimensional symmetry enhancement by exceptional simple lie superalgebras}

\subsection{Outline}

The paper is organized as follows. The first section is the present introduction.

In section 2 we begin by recalling descriptions of minimal twists of eleven dimensional supergravity \cite{} and the abelian six-dimensional $\mc N=(2,0)$ \cite{} and three-dimensional $\mc N=8$ \cite{} superconformal field theories.
